\documentclass[11pt]{article}
\usepackage[left = 1cm,
			top = 1cm,
			right = 1cm,
			bottom = 1cm,
			a4paper]{geometry}
\usepackage[usenames, dvipsnames]{xcolor}
\usepackage[colorlinks = true, 
			linkcolor = black,
			urlcolor = black,
			anchorcolor = blue,
			citecolor = blue]{hyperref}
\usepackage{titlesec}
\usepackage[absolute]{textpos}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage{blindtext}
\usepackage{lipsum}
\usepackage{amsmath}
\usepackage{tcolorbox}
\usepackage{fontawesome}

\parindent 0pt
\pagestyle{empty}
\author{Abhay Maurya}

\begin{document}

	\LARGE{\textbf{Abhay Maurya}}
	\small
	\hfill
        (+91) 8707445762 \\
    4\textsuperscript{th} Year Integrated Student
    \hfill
        \href{mailto:maurya.08abhay@gmail.com}{\color{blue}maurya.08abhay@gmail.com}\\
    \hfill
        Computer Science and Engineering
    \hfill
        \href{https://www.linkedin.com/in/abhay8/}{\color{blue}linkedin.com/in/abhay8}\\
    \hfill
    National Institute of Technology Hamirpur
    \hfill
     	\href{https://github.com/Abhay811}{\color{blue}github.com/Abhay811}\\
    
    \vspace{4pt}
    \textbf{\large{Work Experience}}
    	\vspace{5pt}
    	\hrule \hrule
    	\vspace{4pt}
		\textbf{Khel Gully Gaming Pvt. Ltd.}
		\href{https://drive.google.com/file/d/1pzh4hYnkCkqSkFvYFnbP_ma4imH4uvEk/view?usp=sharing}{\color{blue}\text{\{Certificate\}}}
		\hfill
		\text{Work from home}\\
		\textit{SDE Intern}
		\hfill
		\textit{March 2022 - Present}
		\vspace{-2pt}
		\begin{itemize}
			\setlength{\itemsep}{0pt}
			\setlength{\parskip}{0pt}
			\setlength{\parsep}{0pt}
			\item Designed APIs using \textit{Sql} and \textit{Sequelize}, wrote filter and pagination queries for APIs, Integrated \textit{Cashfree} payouts for payment transfer.
		\end{itemize}
    	
    	\textbf{WizWack Studios Pvt. Ltd.}
    	\href{https://drive.google.com/file/d/14XoMt2XU2isepkzis08b2grJz6ahqw1-/view?usp=sharing}{\color{blue}\text{\{Certificate\}}}
    	\hfill
    	\text{Work from home}\\
    	\textit{Full Stack Developer}
    	\hfill
    	\textit{September 2021 - March 2022}
    	\vspace{-2pt}
    	\begin{itemize}
    		\setlength{\itemsep}{0pt}
        	\setlength{\parskip}{0pt}
        	\setlength{\parsep}{0pt}
    		\item Added layouts and new designs, used \textit{\textbf{firebase deep-links}}, implemented client-client connection using \textit{\textbf{Socket.io}}.
    		\item Worked on \textit{\textbf{Event-driven Architecture}}, used \textit{\textbf{Kafka}}. Integrated youtube and twitch apis, and implemented twitch webhooks with the help of \textit{\textbf{ngrok}} and \textit{\textbf{Redis}} database. 
    		\item Integrated \textit{\textbf{Cashfree}} Payment Gateway and implemented micro-services using \textit{\textbf{firebase}} cloud functions for a game.
    		
    	\end{itemize}
    \textbf{\large{Education}}
    	\vspace{5pt}
    	\hrule \hrule
    	\vspace{-4pt}
    	\begin{itemize}
    		\setlength{\itemsep}{4pt}
        	\setlength{\parskip}{0pt}
        	\setlength{\parsep}{4pt}
        	\item \textbf{National Institute of Technology Hamirpur} \hfill Himachal Pradesh, India\\
        	\textsl{Integrated BTech $+$ MTech.} \textit{CGPA : 8.3/10}  (till 7\textsuperscript{th} Sem)
        	\hfill 
        	\textit{July 2018 - Present}
        	\item \textbf{Rani Laxmi Bai Memorial School} (CBSE) \hfill Lucknow, India\\
        	\textsl{Intermediate(12\textsuperscript{th}) } \textit{Percentage: 84.8\%}  \hfill 
        	\textit{April 2015 - March 2017}
    	\end{itemize}
    \vspace{2pt}
    \textbf{\large{Technical Skills}}
    	\vspace{5pt}
    	\hrule \hrule
    	\vspace{4pt}
    	\textbf{Languages \& Tools:} C, C++, Java, Python, JavaScript, Node.js, R, RStudio, Kotlin, SQL, Docker, Android Studio, Jupyter, Firebase, Git, \LaTeX\\
        \textbf{Certifications \& Training:} \href{https://drive.google.com/file/d/1mir_TBy9GinXpSU3H-8LyYn68GkcM62f/view?usp=sharing}{Neural Networks and Deep Learning}, \href{https://drive.google.com/file/d/18cQMPfNLtvY4-Ozh7hZnUIDKYh9tRYPG/view?usp=sharing}{Convolutional Neural Networks}, \href{https://drive.google.com/file/d/13L4JKQ1pwLG9YVevPVZLNRLUeZWGkvyU/view?usp=sharing}{Machine Learning}, \href{https://drive.google.com/file/d/1Hp5dvhNVz9FvjQ6Y4vIVZldKpb8m8LCp/view?usp=sharing}{Android Development}, Core Java\\
        %\textbf{Soft Skills:} Teamwork, Leadership, Mutual-Respect\\
   
    \textbf{\large{Projects}}
		\vspace{5pt}
    	\hrule \hrule
    	\vspace{4pt}    	
    	\hspace{8pt}
    	\textbf{Weather App}
    	\href{https://github.com/Abhay811/Weather-App}{\color{blue}\text{\{link to project\}}}
    	\hfill
        \textit{September 2021}
        \vspace{-6pt}
        \begin{itemize}
        	\setlength{\itemsep}{0pt}
        	\setlength{\parskip}{0pt}
        	\setlength{\parsep}{0pt}
        	\item Build a mobile application using Kotlin in Android, that shows weather condition of user's location area and user can search different locations on app to see weather of other locations.
        	\item Implemented room database to store weather condition of user's location and other locations that user want, so to show weather if user is offline.
        \end{itemize}
    	\hspace{8pt}
    	\textbf{Sudoku Puzzle Solver and OCR}
    	\href{https://github.com/Abhay811/Sudoku_solver}{\color{blue}\text{\{link to project\}}}
    	\hfill
    	\textit{June 2021}
    	\vspace{-6pt}
       	\begin{itemize}
        	\setlength\itemsep{0pt}
        	\setlength\parskip{0pt}
        	\setlength\parsep{0pt}
        	\item  Designed Convolutional Neural Network (CNN) to OCR the digits(0 - 9) of the MNIST dataset
        	\item Deployed trained Model with accuracy of 98\% to the input image containing Sudoku puzzle and Demonstrated the result to original image in form of 9 x 9 grid.
        \end{itemize}
    	\hspace{8pt}
    	\textbf{Onlie Examination System}
    	\href{https://github.com/Abhay811/Advanced-Online-Examination}{\color{blue}\text{\{link to project \}}}
    	\hfill
    	\textit{Feb 2021 - April 2021}
    	\vspace{-6pt}
    	\begin{itemize}
        	\setlength{\itemsep}{0pt}
        	\setlength{\parskip}{0pt}
        	\setlength{\parsep}{0pt}
        	\item Designed and implemented Desktop Application in 2-person team using Python. Students can create their account and log in and college database will be used to verify. For user verification and signup SMTP module is employed to generate 6-digit OTP
    	\end{itemize}
    	\hspace{8pt}\textbf{Pharmacy Management System}
    	\href{https://github.com/Abhay811/DBMS}{\color{blue}\text{\{link to project\}}}
    	\hfill
    	\textit{August 2020 - Nov 2020}
    	\vspace{-6pt}
    	\begin{itemize}
        	\setlength{\itemsep}{0pt}
        	\setlength{\parskip}{0pt}
        	\setlength{\parsep}{0pt}
        	\item Led team of 3 to implement Desktop Application of Pharmacy using Java
        	\item Designed to streamline workflows associated with drug dispensing, medication adherence, medical billing, inventory management and fulfillment, and customer data collection
        \end{itemize}
    \textbf{\large{Achievements}}
    	\vspace{5pt}
    	\hrule \hrule
    	\vspace{-4pt}
   	    \begin{itemize}
        	\setlength{\itemsep}{0pt}
        	\setlength{\parskip}{0pt}
        	\setlength{\parsep}{0pt}
        	\item Solved 300$+$ problems on \textit{Leetcode}.
        	\item Participated in India Skills Competition (North region) 2021 in \textit{IT Network Systems Administration}.\href{https://drive.google.com/file/d/1nsGsz80LLaZx6pFgHgyKvapQtIfYAGc4/view?usp=sharing}{\color{blue}\text{\{Certificate\}}}
        	\item Secured 3\textsuperscript{rd} position out of 20 teams in Treasure Hunt organized by Chemical Engineering Dept.
        	\item Secured 3\textsuperscript{rd} position out of 15 teams in Boat Making organized by Civil Engineering Dept.
        	\item Recipient of scholarship from GAIL for Higher Studies for 2 years.
        	%\item Selected into Super 100 Kanpur batch 2017 - 18, runs with CSRL (NGO), funded by GAIL, which prepare students for JEE Exams
    	\end{itemize}
    
    \textbf{\large{Additional}}
    	\vspace{5pt}
    	\hrule \hrule
    	\vspace{4pt}
    	\textbf{Languages:} English, Hindi\\
    	\textbf{Hobbies/Interests:} Watching Animes, Reading Technological Advancement, Reading/Watching about Cosmos, Competitive Coding
    
\end{document}